Calculating life expectancy and exploring missingness

### 2016-11-04 Code/1_Explore_Data_v2.Rmd
fix old coding error

table1.whitemale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "White.Male"]), 
                                           dat$Age2[dat$RaceSex == "White.Male"]),2)*100,2)
table1.blackmale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "Black.Male"]), 
                                           dat$Age2[dat$RaceSex == "Black.Male"]),2)*100,2)
table1.whitefemale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "White.Female"]), 
                                           dat$Age2[dat$RaceSex == "White.Female"]),2)*100,2)
table1.blackfemale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "Black.Female"]), 
                                           dat$Age2[dat$RaceSex == "Black.Female"]),2)*100,2)

@@

```{r zero_data, fig.width = 10, fig.height = 5, echo=F}
table2.whitemale <- round(prop.table(table(dat$Count[dat$RaceSex == "White.Male"]==0, 
                                       dat$Age2[dat$RaceSex == "White.Male"]),2)*100,2)
table2.blackmale <- round(prop.table(table(dat$Count[dat$RaceSex == "Black.Male"]==0, 
                                       dat$Age2[dat$RaceSex == "Black.Male"]),2)*100,2)
table2.whitefemale <- round(prop.table(table(dat$Count[dat$RaceSex == "White.Female"]==0, 
                                       dat$Age2[dat$RaceSex == "White.Female"]),2)*100,2)
table2.blackfemale <- round(prop.table(table(dat$Count[dat$RaceSex == "Black.Female"]==0, 
                                       dat$Age2[dat$RaceSex == "Black.Female"]),2)*100,2)

@@

table3.whitemale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "White.Male"]==T, 
                                      dat$Age2[dat$RaceSex == "White.Male"]),2)*100,2)
table3.blackmale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "Black.Male"]==T, 
                                       dat$Age2[dat$RaceSex == "Black.Male"]),2)*100,2)
table3.whitefemale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "White.Female"]==T, 
                                       dat$Age2[dat$RaceSex == "White.Female"]),2)*100,2)
table3.blackfemale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "Black.Female"]==T, 
                                       dat$Age2[dat$RaceSex == "Black.Female"]),2)*100,2)

>>>>

table1.whitemale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "White Male"]), 
                                           dat$Age2[dat$RaceSex == "White Male"]),2)*100,2)
table1.blackmale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "Black Male"]), 
                                           dat$Age2[dat$RaceSex == "Black Male"]),2)*100,2)
table1.whitefemale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "White Female"]), 
                                           dat$Age2[dat$RaceSex == "White Female"]),2)*100,2)
table1.blackfemale <- round(prop.table(table(is.na(dat$Count[dat$RaceSex == "Black Female"]), 
                                           dat$Age2[dat$RaceSex == "Black Female"]),2)*100,2)

@@

```{r zero_data, fig.width = 10, fig.height = 5, echo=F}
table2.whitemale <- round(prop.table(table(dat$Count[dat$RaceSex == "White Male"]==0, 
                                       dat$Age2[dat$RaceSex == "White Male"]),2)*100,2)
table2.blackmale <- round(prop.table(table(dat$Count[dat$RaceSex == "Black Male"]==0, 
                                       dat$Age2[dat$RaceSex == "Black Male"]),2)*100,2)
table2.whitefemale <- round(prop.table(table(dat$Count[dat$RaceSex == "White Female"]==0, 
                                       dat$Age2[dat$RaceSex == "White Female"]),2)*100,2)
table2.blackfemale <- round(prop.table(table(dat$Count[dat$RaceSex == "Black Female"]==0, 
                                       dat$Age2[dat$RaceSex == "Black Female"]),2)*100,2)

@@

table3.whitemale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "White Male"]==T, 
                                      dat$Age2[dat$RaceSex == "White Male"]),2)*100,2)
table3.blackmale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "Black Male"]==T, 
                                       dat$Age2[dat$RaceSex == "Black Male"]),2)*100,2)
table3.whitefemale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "White Female"]==T, 
                                       dat$Age2[dat$RaceSex == "White Female"]),2)*100,2)
table3.blackfemale <- round(prop.table(table(dat$miss_or_zero[dat$RaceSex == "Black Female"]==T, 
                                       dat$Age2[dat$RaceSex == "Black Female"]),2)*100,2)
